---
title: "Problem Set 3"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
psid <- read.csv("psid.csv", header = TRUE)
attach(psid)
library(lmtest)
library(sandwich)
```

#### 1.

```{r}
psid$u74 <- as.numeric(re74 == 0)
psid$u75 <- as.numeric(re75 == 0)
```

#### 2.

```{r}
mean_stat <- aggregate(psid, by = list(treat), mean)
sd_stat <- aggregate(psid, by = list(treat), sd)
stat <- matrix(rep(0, 60), 10, 6)
stat[,1] <- t(mean_stat[2, -c(1, 2, 3)]) 
stat[,3] <- t(mean_stat[1, -c(1, 2, 3)]) 
stat[,2] <- t(sd_stat[2, -c(1, 2, 3)]) 
stat[,4] <- t(sd_stat[1, -c(1, 2, 3)]) 
stat[,5] <- stat[,1] - stat[,3]
stat[,6] <- stat[,5]/sqrt((stat[,2]^2 + stat[,4]^2)/2)
stat
```



#### 3.

```{r}
reg1 <- lm(re78~treat, data = psid)
reg2 <- lm(re78~treat + re74 + re75 + u74 + u75, data = psid)
reg3 <- lm(re78~treat + re74 + re75 + u74 + u75 + education  + married + black + hispanic + age + nodegree, data = psid)

coeftest(reg1, vcov = sandwich)
coeftest(reg2, vcov = sandwich)
coeftest(reg3, vcov = sandwich)
```

The estimate is not robust to the specification, estimated treatment effect is not consistent across specifications.

#### 4.

**i)**

Treatment group mean: (24 + 61)/2 = 42.5

Control group mean: (42 + 33 + 46 + 37)/4 = 39.5

Observed statistic value = 42.5 - 39.5 = 3

**ii)**

Treatment group mean: (24 + 42)/2 = 33

Control group mean: (61 + 33 + 46 + 37)/4 = 44.25

Test statistic = 33 - 44.25 = -11.25

**iii)**

$\frac{6!}{2!(6-2)!} = \frac{6*5}{2*1}$

= 15 different ways of assigning treatment and control

**iv)**

{1, 1, 0, 0, 0, 0} = 3

{1, 0, 1, 0, 0, 0} = -11.25

{1, 0, 0, 1, 0, 0} = -18

{1, 0, 0, 0, 1, 0} = -8.25

{1, 0, 0, 0, 0, 1} = -15

{0, 1, 1, 0, 0, 0} = 16.5

{0, 1, 0, 1, 0, 0} = 9.75

{0, 1, 0, 0, 1, 0} = 19.5

{0, 1, 0, 0, 0, 1} = 12.75

{0, 0, 1, 1, 0, 0} = -4.5

{0, 0, 1, 0, 1, 0} = 5.25

{0, 0, 1, 0, 0, 1} = -1.5

{0, 0, 0, 1, 1, 0} = -1.5

{0, 0, 0, 1, 0, 1} = -8.25

{0, 0, 0, 0, 1, 1} = 1.5

```{r, eval = FALSE}
distribution <- as.numeric(list(3, -11.25, -18, -8.25, -15, 16.5, 9.75, 19.5, 12.75, -4.5, 5.25, -1.5, -1.5, -8.25, 1.5))
hist(distribution, breaks = 30)
```

**v)**

Proportion = 6/15 = 0.4

**vi)**

2-sided p-value = 0.4*2 = 0.8

#### 5.

You cannot estimate the treatment effect correctly by comparing the mean difference since the treatment is not randomly assigned. This makes the presence of confounders and selection bias a serious issue, which would lead to an inaccurate ATE. Some possible confounders are:

- Income/socioeconomic status: Individuals that have a low income might be more likely to smoke. They are unable to afford high quality healthcare, which could lead to a higher disease rate.

- Age: Older individuals might be more likely to smoke. They have a weaker immune system, which could lead to a higher disease rate. 

- Occupation: Individuals that work in high-risk jobs (i.e. construction) might be more likely to smoke. A higher rate of injury while working could lead to a higher disease rate.

#### 6.

**i)**

$$E[Y_i|D_i = 1, x] - E[Y_i|D_i = 0, x] = E[Y_i(1)|D_i = 1, x] - E[Y_i(0)|D_i = 0, x] $$

$$= E[Y_i(1)|D_i = 1, x] - E[Y_i(0)|D_i = 1, x] + E[Y_i(0)|D_i = 1, x] - E[Y_i(0)|D_i = 0, x] $$

$$= E[Y_i(1) - Y_i(0)|D_i = 1, x] + (E[Y_i(0)|D_i = 1, x] - E[Y_i(0)|D_i = 0, x]) $$

where $(E[Y_i(0)|D_i = 1, x] - E[Y_i(0)|D_i = 0, x])$ equals the selection bias 

**ii)**

Selection bias can go away under the unconfoundedness assumption.

#### 7.

**i)**

Old: ATE = 30 - 19 = 11

Mid-aged: ATE = 26 - 21 = 5

Young: ATE = 22 - 18 = 4

**ii)**

Old: 25 + 140 = 165

Mid-aged: 90 + 170 = 260

Young: 235 + 155 = 390

Total: 165 + 260 + 390 = 815

ATE = (165/815)\*11 + (260/815)\*5 + (390/815)*4 = 5.736196
