---
title: "Problem Set 5"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
eitc <- read.csv("eitc.csv", header = TRUE)
attach(eitc)
```

#### 1.

```{r}
eitc$posttreat <- (eitc$year >= 1994)*1
eitc$anykids <- (eitc$children != 0)*1
head(eitc, 5)
```

#### 2.

```{r}
mean(eitc[which(eitc$posttreat == 0 & eitc$anykids == 0),'work'])

mean(eitc[which(eitc$posttreat == 0 & eitc$anykids == 1),'work'])

mean(eitc[which(eitc$posttreat == 1 & eitc$anykids == 0),'work'])

mean(eitc[which(eitc$posttreat == 1 & eitc$anykids == 1),'work'])
```

**i)**

Mean of posttreat = 0 & anykids = 0 is 0.5754597

**ii)**

Mean of posttreat = 0 & anykids = 1 is 0.4459619

**iii)**

Mean of posttreat = 1 & anykids = 0 is 0.5733862

**iv)** 

Mean of posttreat = 1 & anykids = 1 is 0.4907615

#### 3.

```{r}
mean(eitc[which(eitc$posttreat == 1 & eitc$anykids == 1),'work']) - mean(eitc[which(eitc$posttreat == 0 & eitc$anykids == 1),'work'])
```

Effect = 0.04479962 increase in employment for women with children

#### 4.

```{r}
eitc$interact = eitc$posttreat*eitc$anykids
reg = lm(work ~ anykids + posttreat + interact, data = eitc)
summary(reg)
```

DID estimate = 0.046873   

Standard Error = 0.017158

#### 5.

**i)**

$$
y_i^* = \beta_1 + \beta_2x_i + u_i + v_i
$$

$$
y_i^* = \beta_1 + \beta_2x_i + u_i^*
$$
where

$$
u_i^* = u_i + v_i
$$

**ii)**
$$
Var(u_i^*) = \sigma^2 + \omega^2 +2Cov(u_i, v_i)
$$

$v_i$ is independent of $u_i$, so $Cov(u_i, v_i) = 0$

$$
Var(u_i^*) = \sigma^2 + \omega^2
$$

**iii)**

$$
E(u_i|x_i) = 0
$$

$v_i$ and $x_i$ are independent, so $E(v_i|x_i) = 0$

$E(u_i|x_i) + E(v_i|x_i) = 0$

$E(u_i + v_i|x_i) = 0$

$E(u_i^*|x_i) = 0$

**iv)**

$$Cov(x_i,u_i^*) = Cov(x_i,u_i + v_i$$

OLS estimator is unbiased because $E(u_i^*|x_i) = 0$

**v)**

$$
\hat{\beta} = \beta + \frac{Cov(x_i, u_i^*)}{Var(x_i)}
$$
$E(u_i^*|x_i) = 0$, so $Cov(x_i, u_i^*) = 0$

$$
\hat{\beta} = \beta
$$

OLS estimator is consistent


#### 6.

**i)**


$y_{1i} = \gamma y_{2i} + \beta_1x_{1i} + \beta_2x_{2i} + u_i$

$y_{2i} = \delta y_{1i} + \beta_3x_{3i} + v_i$



$y_{1i} = \gamma [\delta y_{1i} + \beta_3x_{3i} + v_i] + \beta_1x_{1i} + \beta_2x_{2i} + u_i$

$y_{1i} = \gamma \delta y_{1i} + \gamma \beta_3x_{3i} + \gamma v_i + \beta_1x_{1i} + \beta_2x_{2i} + u_i$

$y_{1i} - \gamma \delta y_{1i} = \gamma \beta_3x_{3i} + \gamma v_i + \beta_1x_{1i} + \beta_2x_{2i} + u_i$

$y_{1i}(1 - \gamma \delta) = \gamma \beta_3x_{3i} + \gamma v_i + \beta_1x_{1i} + \beta_2x_{2i} + u_i$

$y_{1i} = \frac{1}{(1 - \gamma \delta)}[\beta_1x_{1i} + \beta_2x_{2i} + \gamma \beta_3x_{3i} + (\gamma v_i + u_i)]$

$y_{1i} = \frac{\beta_1}{(1 - \gamma \delta)}x_{1i} + \frac{\beta_2}{(1 - \gamma \delta)}x_{2i} + \frac{\gamma \beta_3}{(1 - \gamma \delta)}x_{3i} + \frac{\gamma v_i + u_i}{(1 - \gamma \delta)}$


$y_{2i} = \delta[\gamma y_{2i} + \beta_1x_{1i} + \beta_2x_{2i} + u_i] + \beta_3x_{3i} + v_i$

$y_{2i} = \delta\gamma y_{2i} + \delta\beta_1x_{1i} + \delta\beta_2x_{2i} + \delta u_i + \beta_3x_{3i} + v_i$

$y_{2i} -\delta\gamma y_{2i} =  \delta\beta_1x_{1i} + \delta\beta_2x_{2i} + \delta u_i + \beta_3x_{3i} + v_i$

$y_{2i}(1 -\delta\gamma) =  \delta\beta_1x_{1i} + \delta\beta_2x_{2i} + \delta u_i + \beta_3x_{3i} + v_i$

$y_{2i} =  \frac{1}{(1 -\delta\gamma)}[\delta\beta_1x_{1i} + \delta\beta_2x_{2i} + \beta_3x_{3i} + (\delta u_i + v_i)]$

$y_{2i} =  \frac{\delta\beta_1}{(1 -\delta\gamma)}x_{1i} + \frac{\delta\beta_2}{(1 -\delta\gamma)}x_{2i} + \frac{\beta_3}{(1 -\delta\gamma)}x_{3i} + \frac{\delta u_i + v_i}{(1 -\delta\gamma)}$


$\pi_{11} = \frac{\beta_1}{(1 - \gamma \delta)}$

$\pi_{12} = \frac{\beta_2}{(1 - \gamma \delta)}$

$\pi_{13} = \frac{\gamma \beta_3}{(1 - \gamma \delta)}$

$\pi_{21} = \frac{\delta\beta_1}{(1 -\delta\gamma)}$

$\pi_{22} = \frac{\delta\beta_2}{(1 -\delta\gamma)}$

$\pi_{23} = \frac{\beta_3}{(1 -\delta\gamma)}$

$\tilde{u}_i = \frac{\gamma v_i + u_i}{(1 - \gamma \delta)}$

$\tilde{v}_i = \frac{\delta u_i + v_i}{(1 -\delta\gamma)}$


**ii)**

Consistent estimates of $\pi$ indicates that $Corr(\pi, x_i) \neq 0$ and $Corr(\pi, u_i) = 0$

$\pi_{13}x_{3i} = \frac{\gamma \beta_3}{(1 - \gamma \delta)}x_{3i}$, so $Corr(\gamma, x_i) \neq 0$ while there is no correlation with the error term, so $Corr(\gamma, u_i) = 0$

**iii)**

No

**iv)**

Instrument relevance and instrument exogeneity.

**v)**

By using instrumental variables that are uncorrelated with the error term, it is possible to estimate the model parameter $\delta$. These instrumental variables are correlated to the endogenous variables (which are correlated to the error term) but by itself has no correlation with the error term.
