---
title: "Problem Set 2"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval = FALSE}
lalonde <- read.csv("lalonde.csv", header = TRUE)
attach(lalonde)

install.packages("lmtest")
library(lmtest)

install.packages("sandwich")
library(sandwich)
```

#### 1.

```{r, eval = FALSE}
prob1 <- lm(re78 ~ treat)
summary(prob1)
```

Average Treatment Effect: 1793.6
S.E.: 632.9
Confidence Interval: (553.116, 3034.084)

#### 2.

```{r, eval = FALSE}
coeftest(prob1, vcov = sandwich)
```

Average Treatment Effect: 1793.61
S.E.: 669.33
Confidence Interval: (481.7232, 3105.4968)

#### 3.

**i)**

True

Given that 

E(u∣X)    =   0,

Definition of Covariance,
            
Cov(X,u)    =   E[(X − E[X])(u − E[u])]

=   E[Xu − XE[u] − E[X]u + E[X]E[u]]
            
=   E[Xu] − E[X]E[u] − E[X]E[u] + E[X]E[u]
            
=   E[Xu] − E[X]E[u]
            
=   E[Xu] − E[X]E[E[u∣X]]
            
=   E[Xu] − E[X]E[0]
                
=   E[Xu]
            
=   E[E[Xu∣X]]
            
=   E[XE[u∣X]]
            
=   E[X*0]
                
=   E[0]
                
=   0

**ii)**



Given that 

E[uX] = 0,
    
E[u<sup>2</sup>X<sup>2</sup>] = E[u\*u\*X*X]


**iii)**



#### 4.

**i)**

$$\alpha = \frac{(\sum Y)(\sum X^2) - (\sum X)(\sum XY)}{n(\sum X^2) - (\sum X)^2}$$

$$\alpha = \frac{(219.719)(51.075) - (31.47)(349.486)}{24(51.075) - (31.47)^2}$$

$\alpha$ = 0.950664121

$$\beta = \frac{n(\sum XY) - (\sum X)(\sum Y)}{n(\sum X^2) - (\sum X)^2}$$

$$\beta = \frac{24(349.486) - (31.47)(219.719)}{24(51.075) - (31.470)^2}$$

$\beta$ = 6.256849733

**ii)**

u<sub>i</sub> = Y - $\alpha$ - $\beta$X

$$\sum u^2 = \sum (Y - \alpha - \beta X)^2$$

$$= \sum Y^2+\alpha^2n + \beta^2\sum X^2−2(\beta\sum XY - \alpha \beta\sum X + \alpha\sum Y)$$

$$= 2396.504+0.950664121^2*24 + 6.256849733^2*51.075−2(6.256849733*349.486 - 0.950664121*6.256849733*31.470 + 0.950664121*219.719)$$


$\sum u^2$ = 0.943644

**iii)**

E[X] = 31.47/24 = 1.31125

E[Y] = 219.719/24 = 9.15495833333

u<sub>i</sub> = Y - $\alpha$ - $\beta$X

= 9.15495833333 - 0.950664121 - 6.256849733*1.31125

u<sub>i</sub> = 0

0.950664121 + 6.256849733*100 - 0

Total Consumption = 626.6356374 thousand pounds

#### 5.

**i)**

Y = $/alpha$ + $/beta$D + u<sub>i</sub>

$/alpha$ = Y - $/beta$D - u<sub>i</sub>

**ii)**



**iii)**


