---
title: "Problem Set 2"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval = FALSE}
lalonde <- read.csv("lalonde.csv", header = TRUE)
attach(lalonde)

install.packages("lmtest")
library(lmtest)

install.packages("sandwich")
library(sandwich)
```

#### 1.

```{r, eval = FALSE}
prob1 <- lm(re78 ~ treat)
summary(prob1)
```

Average Treatment Effect: 1793.6
S.E.: 632.9
Confidence Interval: (553.116, 3034.084)

#### 2.

```{r, eval = FALSE}
coeftest(prob1, vcov = sandwich)
```

Average Treatment Effect: 1793.61
S.E.: 669.33
Confidence Interval: (481.7232, 3105.4968)

#### 3.

**i)**

True

Given that 

E(u∣X)    =   0,

Definition of Covariance,
            
Cov(X,u)    =   E[(X − E[X])(u − E[u])]

=   E[Xu − XE[u] − E[X]u + E[X]E[u]]
            
=   E[Xu] − E[X]E[u] − E[X]E[u] + E[X]E[u]
            
=   E[Xu] − E[X]E[u]
            
=   E[Xu] − E[X]E[E[u∣X]]
            
=   E[Xu] − E[X]E[0]
                
=   E[Xu]
            
=   E[E[Xu∣X]]
            
=   E[XE[u∣X]]
            
=   E[X*0]
                
=   E[0]
                
=   0

**ii)**

False

For,

E[uX] = 0,
    
unless all values of u = 0, 

E[u<sup>2</sup>X<sup>2</sup>]

will always result in a positive number as both values are being squared.

**iii)**

True

E(u∣X)

E[uX<sup>3</sup>]

= E[E[X<sup>3</sup>u∣X]

= E[X<sup>3</sup>E[u∣X]

= E[X<sup>3</sup>*0]

= 0

#### 4.

**i)**

$$\alpha = \frac{(\sum Y)(\sum X^2) - (\sum X)(\sum XY)}{n(\sum X^2) - (\sum X)^2}$$

$$\alpha = \frac{(219.719)(51.075) - (31.47)(349.486)}{24(51.075) - (31.47)^2}$$

$\alpha$ = 0.950664121

$$\beta = \frac{n(\sum XY) - (\sum X)(\sum Y)}{n(\sum X^2) - (\sum X)^2}$$

$$\beta = \frac{24(349.486) - (31.47)(219.719)}{24(51.075) - (31.470)^2}$$

$\beta$ = 6.256849733

**ii)**

u<sub>i</sub> = Y - $\alpha$ - $\beta$X

$$\sum u^2 = \sum (Y - \alpha - \beta X)^2$$

$$= \sum Y^2+\alpha^2n + \beta^2\sum X^2−2(\beta\sum XY - \alpha \beta\sum X + \alpha\sum Y)$$

$$= 2396.504+0.950664121^2*24 + 6.256849733^2*51.075−2(6.256849733*349.486 - 0.950664121*6.256849733*31.470 + 0.950664121*219.719)$$


$\sum u^2$ = 0.943644

**iii)**

E[X] = 31.47/24 = 1.31125

E[Y] = 219.719/24 = 9.15495833333

u<sub>i</sub> = Y - $\alpha$ - $\beta$X

= 9.15495833333 - 0.950664121 - 6.256849733*1.31125

u<sub>i</sub> = 0

0.950664121 + 6.256849733*100 - 0

Total Consumption = 626.6356374 thousand pounds

#### 5.

**i)**

Given,

$$argmin \sum_{i=1}^{N} (Y - \alpha - \beta D)^2$$

Using the chain rule, where u = $Y - \alpha - \beta D$

we get 

$\frac{dW}{d\alpha} = \sum_{i=1}^{N} -2(Y - \alpha - \beta D) = 0$

and 

$\frac{dW}{d\beta} = \sum_{i=1}^{N} -2D(Y - \alpha - \beta D) = 0$

for $\alpha$,

$\sum_{i=1}^{N} -2(Y - \alpha - \beta D) = 0$

$-2*\sum_{i=1}^{N} (Y - \alpha - \beta D) = 0$

$\sum_{i=1}^{N} (Y - \alpha - \beta D) = 0$

$N(\bar Y - \alpha - \beta \bar D) = 0$

$(\bar Y - \alpha - \beta \bar D) = 0$

$\alpha = \bar Y - \beta \bar D$

for $\beta$,

$\sum_{i=1}^{N} -2D(Y - \alpha - \beta D) = 0$

$-2\sum_{i=1}^{N} D(Y - \alpha - \beta D) = 0$

$\sum_{i=1}^{N} D(Y - \alpha - \beta D) = 0$

$\sum_{i=1}^{N} DY - \alpha D - \beta D^2 = 0$

$\sum_{i=1}^{N} DY - (\bar Y - \beta \bar D)D - \beta D^2 = 0$

$\sum_{i=1}^{N} DY - D\bar Y + \beta \bar DD - \beta D^2 = 0$

$\sum_{i=1}^{N} DY - \sum_{i=1}^{N} D\bar Y + \sum_{i=1}^{N} \beta \bar DD - \sum_{i=1}^{N} \beta D^2 = 0$

$\sum_{i=1}^{N} DY - \bar Y\sum_{i=1}^{N} D + \beta \bar D\sum_{i=1}^{N} D - \beta\sum_{i=1}^{N} D^2 = 0$

$\sum_{i=1}^{N} DY - \bar Y\sum_{i=1}^{N} D = \beta (\sum_{i=1}^{N} D^2 - \bar D\sum_{i=1}^{N} D)$

$\beta = \frac{\sum_{i=1}^{N} DY - \bar Y\sum_{i=1}^{N} D} {\sum_{i=1}^{N} D^2 - \bar D\sum_{i=1}^{N} D}$

$\beta = \frac{\sum_{i=1}^{N} DY - \frac{1}{N}\sum_{i=1}^{N}Y\sum_{i=1}^{N} D} {\sum_{i=1}^{N} D^2 - \frac{1}{N}\sum_{i=1}^{N}D\sum_{i=1}^{N} D}$

$\beta = \frac{\sum_{i=1}^{N} DY - \frac{1}{N}\sum_{i=1}^{N}Y\sum_{i=1}^{N} D} { \sum_{i=1}^{N} D^2 - \frac{1}{N}(\sum_{i=1}^{N}D)^2}$

**ii)**

$\alpha$ is the same

for $\beta$, from the previous problem we had

$\beta = \frac{\sum_{i=1}^{N} DY - \bar Y\sum_{i=1}^{N} D} {\sum_{i=1}^{N} D^2 - \bar D\sum_{i=1}^{N} D}$

$\beta = \frac{\sum_{i=1}^{N} DY - \sum_{i=1}^{N} D\bar Y} {\sum_{i=1}^{N} D^2 - \sum_{i=1}^{N} D\bar D}$

using these steps,

$\sum_{i=1}^{N}(D - \bar D)^2 = \sum_{i=1}^{N}(D^2 - 2D\bar D + \bar D^2)$

$=\sum_{i=1}^{N}D^2 - \sum_{i=1}^{N}2D\bar D + \sum_{i=1}^{N}\bar D^2$

$=\sum_{i=1}^{N}D^2 - 2\bar D\sum_{i=1}^{N}D + \bar D^2\sum_{i=1}^{N}1$

$=\sum_{i=1}^{N}D^2 - 2N\bar D^2 + N\bar D^2$

$=\sum_{i=1}^{N}D^2 - N\bar D^2$

$=\sum_{i=1}^{N}D^2 - \sum_{i=1}^{N}D\bar D$

$\sum_{i=1}^{N}(D - \bar D)(Y - \bar Y) = \sum_{i=1}^{N}(DY - D\bar Y - \bar D Y + \bar D\bar Y)$

$=\sum_{i=1}^{N}DY - \sum_{i=1}^{N}D\bar Y - \sum_{i=1}^{N}\bar D Y + \sum_{i=1}^{N}\bar D\bar Y$

$=\sum_{i=1}^{N}DY - \sum_{i=1}^{N}D\bar Y - \bar D \sum_{i=1}^{N}Y + \bar D\bar Y\sum_{i=1}^{N}1$

$=\sum_{i=1}^{N}DY - \sum_{i=1}^{N}D\bar Y - N\bar D \bar Y  + N\bar D\bar Y$

$=\sum_{i=1}^{N}DY - \sum_{i=1}^{N}D\bar Y$

shows that

$\beta = \frac{\sum_{i=1}^{N} (D - \bar D)(Y - \bar Y)} {\sum_{i=1}^{N} (D - \bar D)^2}$

**iii)**

$\beta = \frac{1}{N_1}\sum_{i=1}^{N}YD - \frac{1}{N_0}\sum_{i=1}^{N}Y(1-D)$

$= \frac{\sum_{i=1}^{N}(YD)}{\sum_{i=1}^{N}D} - \frac{\sum_{i=1}^{N}(Y(1-D))}{\sum_{i=1}^{N}(1-D)}$

$= \frac{\sum_{i=1}^{N}(1-D)\sum_{i=1}^{N}(YD) - \sum_{i=1}^{N}D \sum_{i=1}^{N}(Y(1-D))}{\sum_{i=1}^{N}D\sum_{i=1}^{N}(1-D)}$

$= \frac{N\sum_{i=1}^{N} YD - \sum_{i=1}^{N} D \sum_{i=1}^{N} Y}{N \sum_{i=1}^{N} D - (\sum_{i=1}^{N} D)^2}$

$= \frac{\sum_{i=1}^{N} YD - \frac{1}{N}\sum_{i=1}^{N} D \sum_{i=1}^{N} Y}{\sum_{i=1}^{N} D - \frac{1}{N}(\sum_{i=1}^{N} D)^2}$

$\beta = \frac{\sum_{i=1}^{N} DY - \frac{1}{N}\sum_{i=1}^{N}Y\sum_{i=1}^{N} D} { \sum_{i=1}^{N} D^2 - \frac{1}{N}(\sum_{i=1}^{N}D)^2}$

is equivalent to

$\beta = \frac{\sum_{i=1}^{N} (D - \bar D)(Y - \bar Y)} {\sum_{i=1}^{N} (D - \bar D)^2}$
